GeoSPARQL 1.1: an almost decadal update to the most important geospatial LOD standard

### 2021-03-08 manuscript.tex
Update on Overleaf.

\author{
    Nicholas J. Car\inst{1,2}\orcidID{0000-0002-8742-7730} \and \\
    Timo Homburg\inst{3}\orcidID{1111-2222-3333-4444} \and \\
    Third Author\inst{3}\orcidID{2222-3333-4444-5555}
}

@@

\institute{SURROUND Australia Pty Ltd., Brisbane Australia \and
Australian National University, Canberra Australia
\email{nicholas.car@surroundaustralia.com}\\
\url{https://surroundaustralia.com} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}

>>>>

\author{
    Nicholas J. Car\inst{1,2}\orcidID{0000-0002-8742-7730} \and \\
    Timo Homburg\inst{3}\orcidID{0000-0002-9499-5840} \and \\
    Third Author\inst{3}\orcidID{2222-3333-4444-5555}
}

@@

\institute{SURROUND Australia Pty Ltd., Brisbane Australia \and
Australian National University, Canberra Australia \and Mainz University Of Applied Sciences, Germany
\email{nicholas.car@surroundaustralia.com, timo.homburg@hs-mainz.de}\\
\url{https://surroundaustralia.com} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
